Measuring neutron star tidal deformability with Advanced LIGO: a Bayesian analysis of mixed binary observations

### 2016-06-30 Paper/paper.tex
adding script ot sample astrophys pop

\textbf{Multiple identical sources at low SNR: }\label{s2:identical_multiple}
% 
We start with a crude calculation which tells us that approximately $8$ (or $16$) 
observations
of NSBH signals with $\rho\geq 10$ distributed uniformly in effective volume, would
give us similarly accurate a measurement of $\lambdans$ as would a single detection
with $\rho=50$ (or $\rho=70$).

@@

$\deff^\mathrm{max}$. The radius of this sphere is set by the lowest SNR that 

@@

given by

>>>>

\red{Add segway into multiple observations. Point out that all NSs share the same
$\lambdans(\mns)$, so multiple signals can be combined the measure the common $\lambdans$.}

\textbf{Multiple identical sources at low SNR: }\label{s2:identical_multiple}
% 
\red{Simplify presentation: remove (or 16) and (or $\rho=70$) etc. ADd sentence:
similarly, $16,\rho=10$ events are comparable to one $\rho=70$ event.}
% 
We start with a crude calculation which tells us that approximately $8$ (or $16$) 
observations
of NSBH signals with $\rho\geq 10$ distributed uniformly in effective volume, would
give us similarly accurate a measurement of $\lambdans$ as would a single detection
with $\rho=50$ (or $\rho=70$).

\dred{%

@@

$\deff^\mathrm{max}$.}
\red{These sentences are distracting. I suggest to simply say 'sources
uniform in volume'. Probably not necessary to discuss effective distance
at all. If so, then do so in a footnote.}
\red{Explain (or state, if explanation is trivial} that uniform in volume,
uniform in orientation, is equivalent to uniform in effective volume.}
\dred{%
The radius of this sphere is set by the lowest SNR that 

@@

given by}
\red{..into $I$ shells of same radial thickness. The radius at the middle of the}
